Fast Bayesian Inference for Exoplanet Discovery in Radial Velocity Data

### 2014-11-19 Paper/ms.tex
Updated nu oph figures

The marginal likelihood for our model was
$\log(\mathcal{Z}) \approx -217.04$ and the information
(Kullback-Leibler divergence from the prior to the posterior)
was $\mathcal{H} \approx 80.0$ nats.

>>>>

The marginal likelihood for our model was
$\log(\mathcal{Z}) \approx -217.65$ and the information
(Kullback-Leibler divergence from the prior to the posterior)
was $\mathcal{H} \approx 77.7$ nats.
